Response to the defense feedback

### 2021-06-15 Chapter-3/Chapter-3.tex
Updates from Overleaf

where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation. For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2. However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.

@@

For examples, considering the following x86 code snippet,

\begin{lstlisting}[xleftmargin=.3\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
...
0x0000e781      add dword [local_14h], 1
0x0000e785      cmp dword [local_14h], 4
0x0000e789      jne 0xe7df
0x0000e78b      mov dword [local_14h], 0
...
\end{lstlisting}

@@

where $L$ represents the minimum memory address granularity that an attacker can observe. For example, Flush and Reload can distinguish between different cache lines, which means the value of L is 6 for 64 byte cache line.

>>>>

\noindent where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation. For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2. However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.

@@

For examples, considering the following x86 code snippet.

\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
...
0x0000e781      add dword [local_14h], 1
0x0000e785      cmp dword [local_14h], 4
0x0000e789      jne 0xe7df
0x0000e78b      mov dword [local_14h], 0
...
\end{lstlisting}

@@

\noindent where $L$ represents the minimum memory address granularity that an attacker can observe. For example, Flush and Reload can distinguish between different cache lines, which means the value of L is 6 for 64 byte cache line.

### 2021-06-15 Chapter-4/Chapter-4.tex
Updates from Overleaf

The threat model is similar to our previous work. That is, we assume
an attacker can share some hardware resource with the victim. The attacker has
the ability to probe the victim at any time of the execution. We also assume
an attacker has noise-free observations. The attacker has the access to the victim's
binary executable. The threat mode is similar to
the previous work~\cite{203878,182946,Brotzman19Casym} and can catch most of
the address-based side-channel attacks in the literature.

@@

Let $k$ be one of the possible
value of $K$. The Shannon entropy $H(K)$ is defined as
\begin{displaymath}
    H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
\end{displaymath}

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
uint8_t key[2], t1, t2;
get_key(key);              // 0 <= key[0], key[1] < 256
t1 = key[0] + key[1];
t2 = key[0] - key[1];
if (t1 < 4){               // leakage site A
    foo();    
}                          
if (t2 > 0){               // leakage site B     
    doo();    
}                          
\end{lstlisting}
    \vspace*{-1pt}
    \caption{Side-channel leakage}
    \label{fig:side-channel}
\end{figure}
In this chapter, we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
Therefore, an attacker can have two different observations for each leak site
depending on the value of the $\mathit{key}$: $A$ for function \textsf{foo} is executed,
$\neg A$ for function \textsf{foo} is not executed, $B$ for function \textsf{doo} is
executed, and $\neg B$ for function \textsf{doo} is not executed. Now the
question is how much information can be leaked from the above code if an
attacker knows which branch is executed?

\begin{table}[ht]
    \centering%\small\footnotesize
    \caption{The distribution of observation}\label{shtable}
    %    \resizebox{\columnwidth}{!}{
    \begin{tabular}{l|cc|cc}
        \hline

@@

\textbf{Min Entropy.}
As $p_{A\mathit{max}} = 0.9998$ and $p_{B\mathit{max}} = 0.5$,
with the definition, min-entropy equals to
\begin{align*}
    \mathit{min\text{-}entropy_A} & = -\log_2{0.9998} = 0.000\ \mathrm{bits} \\
    \mathit{min\text{-}entropy_B} & = -\log_2{0.5} = 1.000\ \mathrm{bits}
\end{align*}

\textbf{Max Entropy.}
Depending on the value of key, the code can run two different branches for each leakage site.
Therefore, with the max entropy
definition, both leakage sites leak

@@

\textbf{Shannon Entropy.}
Based on Shannon entropy, the respective amount of information in A and B equals to
    {%\footnotesize
        \begin{align*}
            \mathit{Shannon\text{-}entropy_A} & = -(0.9998*\log_{2}0.9998      \\
                                              & \qquad+ 0.0002*\log_{2}0.0002) \\
                                              & = 0.000\ \mathrm{bits}         \\
            \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5            \\
                                              & \qquad+ 0.5*\log_{2}0.5)       \\
                                              & = 1.000\ \mathrm{bits}
        \end{align*}
    }
In the next section, we will show that these measures work well only
theoretically in a static analysis setting.
Generally, they do not apply to dynamic analysis or real
settings. We will present that the static or theoretical results could be
dramatically different from the real world, and we do need a better method to
quantify the information leakage from a practical point of view.

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
char key[9] = input();
if(strcmp(key, "password"))   // leakage site C
    pass();                   // branch 1
else
    fail();                   // branch 2
\end{lstlisting}
    \vspace*{-10pt}
    \caption{A dummy password checker}
    \label{fig:password-checker}
\end{figure}

@@

However, prior static approaches cannot precisely capture the amount of leakage. According to the definition of Shannon entropy, the leakage will be
$\frac{1}{2^{64}}*\log_{2}\frac{1}{2^{64}} + \frac{2^{64}-1}{2^{64}}
    *\log_{2}\frac{2^{64}-1}{2^{64}} \approx 0$ bits. Max-entropy is defined from the
number of possible observations. Because the program has two
branches, tools based on max-entropy will report the code has a $\log_2{2} = 1$
bit leakage.
Both approaches fail to tell how much information is leaked during the execution
precisely. The problem with existing methods is that they are static-based so
input values and real runtime information are neglected by their approaches.
They assume an attacker runs
the program multiple times with many different or random sensitive inputs. As
shown in Figure~\ref{fig:gap}(a), previous models, both Shannon entropy and max
entropy, give an ``average'' estimate of the information leakage. However, it is
not the typical scenario for an adversary to launch a side-channel attack. When
a side-channel attack happens, the adversary wants to retrieve the sensitive
information, in which case the sensitive information is fixed (e.g., AES keys).
The adversary will run the attack over and over again with fixed input and
guess the value bit by
bit (e.g., Kocher's timing attacks~\cite{kocher1996timing}), as in Figure~\ref{fig:gap}(b). We want to have a
theory for dynamic analysis that if the theory says an attack leaks $x$ bits of
secret information from a side-channel vulnerability, then $x$ should be useful
in estimating the sensitive level of the vulnerability. However, the above
methods all fail in real attack models.
\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter4/RA.pdf}
    \caption{The gap between the real attack and previous models}\label{fig:gap}
\end{figure}

@@

We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be
a finite set of keys. The program also takes known messages $M$ as its input.
During an AES encryption, for example,
$\beta$ is the encryption function. $K$ is the set of all possible AES keys,
and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have
some observations ($O$) of the program. This dissertation only
uses secret-dependent control flows and secret-dependent data
accesses as observations.

With the above definition, we have the following mapping between $\beta$,
$K$, $M$, and $O$:
%\vspace*{-0pt}
\begin{displaymath}
    \beta(K, M) \rightarrow O
\end{displaymath}

@@

\emph{How much uncertainty of $K$ is reduced if an attacker knows $\beta$, $m$, and $o$?}

In information theory, the mutual information (I) is a measure of the mutual
dependence between two variables. Here we use I to describe the
dependence between original sensitive keys ($K$) and attackers' observations ($O$),
which is defined as:

@@

where $p(k_i, o_i)$ is the joint discrete distribution of $K$ and $O$.
Alternatively, the mutual information can also be equivalently expressed as:

@@

$H(K|O)$ is the entropy of $K$ with the condition $O$. It quantifies the
uncertainty of $K$ given the value of $O$. In other word, the conditional
entropy $H(K|O)$ marks the uncertainty about $K$ after an adversary has gained
some observations ($O$).
\begin{equation}
    H(K|O) = - \sum_{o {\in} O} {p(o) \sum_{k {\in} K}{p(k|o)\log_2p(k|o)}}
\end{equation}

In this project, we hope to give a very precise definition of information
leakages. Suppose an attacker runs the target program with one
fixed input, we want to know how much information he can infer by observing the
memory access patterns ($o$). We come to the simple slogan
~\cite{10.1007/978-3-642-00596-1_21} %% where the information
%% leakage equals:
%% \textbf{Initial uncertainty - remaining uncertainty}
that
\begin{align*}
     & \mathit{Information\ leakage} =                                       \\
     & ~~~~ \mathit{Initial\ uncertainty} - \mathit{Remaining\ uncertainty}.
\end{align*}

Next we compare the Eq.~(\ref{eq:2}) with the above slogan, we find $H(K)$
is the $\mathit{Initial\ uncertainty}$ and $H(K|O)$ is $\mathit{Remaining\
        uncertainty}$. During a real attack, the observation ($o$) is known.  Thus we
have $H(K|O) = H(K|o)$.

Therefore, we define the amount of leaked information as
\begin{displaymath}
    Leakage = I(K;o) = H(K) - H(K|o)
\end{displaymath}

For a program ($\beta$) without knowing any domain information, all possible sensitive
inputs should appear equally. Therefore, for any $k \in K$, $p(k) =
    \frac{1}{|K|}$. So we have
$$H(K) = \sum_{k {\in} K}\frac{1}{|K|}\log_2{|K|} = \log_2{|K|}$$
For any $k' \in K \setminus K^o$, $p(k'|o) = 0$. We get
\begin{align*}
    I(K;o) & = - \sum_{k {\in} K^o}{p(k|o)\log_2p(k|o)}                         \\
           & \qquad   - \sum_{k` {\in} (K \setminus K^o)}{p(k'|o)\log_2p(k'|o)} \\
           & = \sum_{k {\in} K^o}\frac{1}{|K^o|}\log_2{|K^o|}                   \\
           & = \log_2{|K^o|}
\end{align*}

\begin{mydef}
    \label{chapter4:def}
    Given a program $\beta$ with the input set $K$,
    an adversary has the observation $o$ when the input $k{\in}K^o$.
    We denote it as
    $$\beta(K^o, m) \rightarrow	o$$

    The amount of leaked information $L_{\beta(k)\rightarrow o}$ based on the observation ($o$) is
    $$L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|}$$
\end{mydef}

The above definition~\cite{AskarovC12} can be understood in an intuitive way. Suppose an attacker
wants to guess a 128-bit encryption key from a program.
Without any domain knowledge,
he can find the key by performing exhaustive search over $2^{128}$ possible keys.
However, the program has a side-channel leakage site. After the program finishes execution, the
attacker get some leaked information and only need to find the key by performing
exhaustive search over $2^{120}$ possible keys. Then we can say that 8 bits of the information
is leaked. In this example, $2^{128}$ is the size of $K$ and $2^{120}$ is the size of $K^o$.

@@

\begin{table}[ht]
    \centering%\small\footnotesize
    \caption{New leakage modeling results}
    \label{shtable2}
    \vspace*{-9pt}
    %    \resizebox{\columnwidth}{!}{
    \begin{tabular}{l|cc|cc}
        \hline

@@

\section{Approximate Model Counting}
\label{MCreasons}
In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and showed how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas. Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$). However, preliminary experiments showed that this approach was far too expensive to use with real-world applications. In this section, we discuss the bottlenecks in this approach and propose a practical solution.

@@

        \item[1] mbedTLS\,2.5  \,~~~~~\item[2] mbedTLS\,2.15 ~\item[3] Monocypher\,3.0 \\
        \item[4] OpenSSL\,0.9.7  ~~~\item[5] OpenSSL\,1.0.2f  \item[6] OpenSSL\,1.0.2k 
        \item[7] OpenSSL\,1.1.0f ~\item[8] OpenSSL\,1.1.1 ~\item[9] OpenSSL\,1.1.1g \\
        \item[10] Libgcrypt\,1.6.1 ~\item[11] Libgcrypt\,1.7.3 \item[12] Libgcrypt\,1.8.5\\
    \end{tablenotes}
    \vspace*{-20pt}

@@

For vulnerabilities that leak less amount of information,
developers are more reluctant to fix them or fixing them unintentionally. For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \textbf{m}. In the updated version, developers make the fixed windows the default option and rewrite most of the function. However, the leakage site still exists in OpenSSL 1.1.1.
\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)                    \
    t=(BN_ULLONG)a*b;                                \
    tt=(t+t)&BN_MASK;                                \
    if (tt < t) c2++;                                \
    t1=(BN_ULONG)Lw(tt);                             \
    t2=(BN_ULONG)Hw(tt);                             \
    c0=(c0+t1)&BN_MASK2;                             \
    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
\end{lstlisting}
    \vspace*{-6pt}
    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
    \label{fig:old_sqr2}
    \vspace*{-8pt}
\end{figure}

>>>>

The threat model in this chapter is similar to the threat model in our previous work from Chapter~\ref{chapter3}. Prior work~\cite{203878,182946,Brotzman19Casym} also shares the same threat model. That is, we assume
an attacker can share some hardware resource with the victim. The attacker has
the ability to probe the victim at any time of the execution. We also assume
an attacker has noise-free observations. The attacker has the access to the victim's
binary executable.  We believe that the majority of address-based side-channel attacks in the literature applies to the thread model.

@@

Let $k$ be one of the possible
value of $K$. The Shannon entropy $H(K)$ is defined as
\begin{displaymath}
    H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k)).
\end{displaymath}

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
uint8_t key[2], t1, t2;
get_key(key);              // 0 <= key[0], key[1] < 256
t1 = key[0] + key[1];
t2 = key[0] - key[1];
if (t1 < 4){               // leakage site A
    foo();    
}                          
if (t2 > 0){               // leakage site B     
    doo();    
}                          
\end{lstlisting}
    \caption{Side-channel leakage}
    \label{fig:side-channel}
\end{figure}
In this chapter, we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
Therefore, an attacker can have two different observations for each leak site
depending on the value of the $\mathit{key}$: $A$ for function \textsf{foo} is executed,
$\neg A$ for function \textsf{foo} is not executed, $B$ for function \textsf{doo} is
executed, and $\neg B$ for function \textsf{doo} is not executed. Now the
question is how much information can be leaked from the above code if an
attacker knows which branch is executed?

\begin{table}[ht]
    \centering%\small\footnotesize
    \caption{The distribution of observations}\label{shtable}
    %    \resizebox{\columnwidth}{!}{
    \begin{tabular}{l|cc|cc}
        \hline

@@

\subsubsection*{Min Entropy}
As $p_{A\mathit{max}} = 0.9998$ and $p_{B\mathit{max}} = 0.5$,
with the definition, min-entropy equals to
\begin{align*}
    \mathit{min\text{-}entropy_A} & = -\log_2{0.9998} = 0.000\ \mathrm{bits} \\
    \mathit{min\text{-}entropy_B} & = -\log_2{0.5} = 1.000\ \mathrm{bits}
\end{align*}

\subsubsection*{Max Entropy}
Depending on the value of key, the code can run two different branches for each leakage site.
Therefore, with the max entropy
definition, both leakage sites leak

@@

\subsubsection*{Shannon Entropy}
Based on Shannon entropy, the respective amount of information in A and B equals to
    {%\footnotesize
        \begin{align*}
            \mathit{Shannon\text{-}entropy_A} & = -(0.9998*\log_{2}0.9998      \\
                                              & \qquad+ 0.0002*\log_{2}0.0002) \\
                                              & = 0.000\ \mathrm{bits}         \\
            \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5 + 0.5*\log_{2}0.5)       \\
                                              & = 1.000\ \mathrm{bits}
        \end{align*}
    }
In the next section, we will show that these measures work well only
theoretically in a static analysis setting.
Generally, they do not apply to dynamic analysis or real
settings. We will present that the static or theoretical results could be
dramatically different from the real world, and we do need a better method to
quantify the information leakage from a practical point of view.

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
char key[9] = input();
if(strcmp(key, "password"))   // leakage site C
    pass();                   // branch 1
else
    fail();                   // branch 2
\end{lstlisting}
    \caption{A dummy password checker}
    \label{fig:password-checker}
\end{figure}

@@

However, prior static approaches cannot precisely capture the amount of leakage. According to the definition of Shannon entropy, the leakage will be
$$\frac{1}{2^{64}}*\log_{2}\frac{1}{2^{64}} + \frac{2^{64}-1}{2^{64}}
    *\log_{2}\frac{2^{64}-1}{2^{64}} \approx 0\, \mathrm{bits}.$$ Max-entropy is defined from the
number of possible observations. Because the program has two
branches, tools based on max-entropy will report the code has a $\log_2{2} = 1.0$
bit leakage.
Both approaches fail to tell how much information is leaked during the execution
precisely. The problem with existing methods is that they are static-based so
input values and real runtime information are neglected by their approaches.
They assume an attacker runs
the program multiple times with many different or random sensitive inputs. As
shown in Figure~\ref{fig:gap}(a), previous models, both Shannon entropy and max
entropy, give an ``average'' estimate of the information leakage. However, it is
not the typical scenario for an adversary to launch a side-channel attack. When
a side-channel attack happens, the adversary wants to retrieve the sensitive
information, in which case the sensitive information is fixed (e.g., AES keys).
The adversary will run the attack over and over again with fixed input and
guess the value bit by
bit (e.g., Kocher's timing attacks~\cite{kocher1996timing}), as in Figure~\ref{fig:gap}(b). We want to have a
theory for dynamic analysis that if the theory says an attack leaks $x$ bits of
secret information from a side-channel vulnerability, then $x$ should be useful
in estimating the sensitive level of the vulnerability. However, the above
methods all fail in real attack models.
\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter4/RA.pdf}
    \caption{The gap between real attacks and previous models}\label{fig:gap}
\end{figure}

@@

We assume a program ($\beta$) has $K$ as its sensitive input. The input $K$ should be
a finite set of keys. The program also takes known messages $M$ as its input.
During an AES encryption, for example,
$\beta$ is the encryption function. Here $K$ is the set of all possible AES keys,
and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have
some observations ($O$) of the program. This dissertation only
uses secret-dependent control flows and secret-dependent data
accesses as observations.

With the above definition, we have the following mapping between $\beta$,
$K$, $M$, and $O$:
%\vspace*{-0pt}
\begin{displaymath}
    \beta(K, M) \rightarrow O.
\end{displaymath}

@@

\
\emph{How much uncertainty of $K$ is reduced if an attacker knows $\beta$, $m$, and $o$?}
\

In information theory, the mutual information (I) is a measure of the mutual
dependence between two variables. Here we use I to describe the
dependence between original sensitive keys ($K$) and attackers' observations ($O$),
which is defined as

@@

\noindent where $p(k_i, o_i)$ is the joint discrete distribution of $K$ and $O$.
Alternatively, the mutual information can also be equivalently expressed as

@@

\noindent where $H(K|O)$ is the entropy of $K$ with the condition $O$. It quantifies the
uncertainty of $K$ given the value of $O$. In other word, the conditional
entropy $H(K|O)$ marks the uncertainty about $K$ after an adversary has gained
some observations ($O$).
\begin{equation}
    H(K|O) = - \sum_{o {\in} O} {p(o) \sum_{k {\in} K}{p(k|o)\log_2p(k|o)}}
\end{equation}

In this research, we hope to give a very precise definition of information
leakages. Suppose an attacker runs the target program with one
fixed input, we want to know how much information he can infer by observing the
memory access patterns ($o$). We come to the simple slogan
~\cite{10.1007/978-3-642-00596-1_21} %% where the information
%% leakage equals:
%% \textbf{Initial uncertainty - remaining uncertainty}
that
\begin{align*}
     & \mathit{Information\ leakage} =                                       \\
     & ~~~~ \mathit{Initial\ uncertainty} - \mathit{Remaining\ uncertainty}.
\end{align*}

Next we compare the Eq.~(\ref{eq:2}) with the above slogan, we find that $H(K)$
is the $\mathit{Initial\ uncertainty}$ and $H(K|O)$ is the $\mathit{Remaining\
        uncertainty}$. During a real attack, the observation ($o$) is known.  Thus we
have $H(K|O) = H(K|o)$.

Therefore, we define the amount of leaked information as
\begin{displaymath}
    Leakage = I(K;o) = H(K) - H(K|o).
\end{displaymath}

For a program ($\beta$) without knowing any domain information, all possible sensitive
inputs should appear equally. Therefore, for any $k \in K$, $p(k) =
    \frac{1}{|K|}$. So we have
$$H(K) = \sum_{k {\in} K}\frac{1}{|K|}\log_2{|K|} = \log_2{|K|}.$$
For any $k' \in K \setminus K^o$, $p(k'|o) = 0$. We get
\begin{align*}
    I(K;o) & = - \sum_{k {\in} K^o}{p(k|o)\log_2p(k|o)}                         \\
           & \qquad   - \sum_{k` {\in} (K \setminus K^o)}{p(k'|o)\log_2p(k'|o)} \\
           & = \sum_{k {\in} K^o}\frac{1}{|K^o|}\log_2{|K^o|}                   \\
           & = \log_2{|K^o|}.
\end{align*}

\begin{mydef}
    \label{chapter4:def}
    Given a program $\beta$ with the input set $K$,
    an adversary has the observation $o$ when the input $k{\in}K^o$.
    We denote it as
    $$\beta(K^o, m) \rightarrow	o.$$

    The amount of leaked information $L_{\beta(k)\rightarrow o}$ based on the observation ($o$) is
    $$L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|}.$$
\end{mydef}

The above definition~\cite{AskarovC12} can be understood in an intuitive way. Suppose an attacker
wants to guess a 128-bit encryption key from a program.
Without any domain knowledge,
he can find the key by performing exhaustive search over $2^{128}$ possible keys.
However, the program has a side-channel leakage site. After the program finishes execution, the
attacker gets some leaked information and only needs to find the key by performing
exhaustive search over $2^{120}$ possible keys. Then we can say that 8 bits of the information
is leaked. In this example, $2^{128}$ is the size of $K$ and $2^{120}$ is the size of $K^o$.

@@

\begin{table}[ht]
    \centering%\small\footnotesize
    \caption{New leakage modeling results}
    \label{shtable2}
    %    \resizebox{\columnwidth}{!}{
    \begin{tabular}{l|cc|cc}
        \hline

@@

\section{Approximate Model Counting}
\label{MCreasons}
In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and showed how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas. Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$). However, some preliminary experiments showed that this approach was far too expensive to use with real-world applications. In this section, we discuss the bottlenecks in this approach and propose a practical solution.

@@

        \item[1] mbedTLS\,2.5  \,~~~~~\item[2] mbedTLS\,2.15 ~\item[3] Monocypher\,3.0 \\
        \item[4] OpenSSL\,0.9.7  ~~~\item[5] OpenSSL\,1.0.2f  \item[6] OpenSSL\,1.0.2k 
        \item[7] OpenSSL\,1.1.0f ~\item[8] OpenSSL\,1.1.1 ~\item[9] OpenSSL\,1.1.1g \\
        \item[10] Libgcrypt\,1.6.1 ~\item[11] Libgcrypt\,1.7.3 \item[12] Libgcrypt\,1.8.5\\
    \end{tablenotes}

@@

For vulnerabilities that leak less amount of information,
developers are more reluctant to fix them or fixing them unintentionally. For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \textbf{m}. In the updated version, developers make the fixed windows the default option and rewrite most of the function. However, the leakage site still exists in OpenSSL 1.1.1.
\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)                    \
    t=(BN_ULLONG)a*b;                                \
    tt=(t+t)&BN_MASK;                                \
    if (tt < t) c2++;                                \
    t1=(BN_ULONG)Lw(tt);                             \
    t2=(BN_ULONG)Hw(tt);                             \
    c0=(c0+t1)&BN_MASK2;                             \
    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
\end{lstlisting}
    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
    \label{fig:old_sqr2}
\end{figure}
